---
title: "CodeBook"
author: "Ghora"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Source Code Data

The data collected from the accelerometers from the Samsung Galaxy S smartphone. 

http://archive.ics.uci.edu/ml/datasets/Human+Activity+Recognition+Using+Smartphones
 

https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip


Data files used for the project

train/X_train.txt
train/y_train.txt
train/subject_train.txt
test/X_test.txt
test/y_test.txt
test/subject_test.txt
features.txt
activity_labels.txt

Transformations

Combined the respective data in training and test data sets corresponding to subject, label and dataset.
Named the columns by transposing the names given in the document features.
Merges the training and the test sets to create one complete data set.
Extracts only the measurements on the mean and standard deviation for each measurement. 
Replaced activity codes with descriptive activity names.
Renamed variable names to be more descriptive.

Clean Tidy dataset

The final tidy dataset (Tidy.txt) contains:
One row per subject and activity combination.
One column for each mean and standard deviation measurement.
180 rows (30 subjects × 6 activities)

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
