---
title: "README"
author: "Ghora"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Read the individual datasets. Then, combine the training and test datasets based on the subject matter. Using the labels given in the feature dataset, name the columns of the combined training and test dataset.  Then merge/combine the columns of all the datasets. Take the subset of the original dataset that contains only the mean and standard deviation (std). Now use the descriptive activities to rename the columns. Now, compute summary statistics for each and write this information in a new dataset.

```{tidy}
library(data.table)
library(dplyr)
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
download.file(url, destfile="UCI HAR Dataset.zip", mode="wb")
#unzip the raw data sets
unzip("UCI HAR Dataset.zip", exdir = "data/projectfiles")
list.files("data/projectfiles/UCI HAR Dataset/train")
#Reading the training tables
train_data <- read.table("data/projectfiles/UCI HAR Dataset/train/X_train.txt")
train_label <- read.table("data/projectfiles/UCI HAR Dataset/train/y_train.txt", col.names = "activity")
subject_train <- read.table("data/projectfiles/UCI HAR Dataset/train/subject_train.txt", col.names = "subject")
#Reading the testing tables
test_data <- read.table("data/projectfiles/UCI HAR Dataset/test/X_test.txt")
test_label <- read.table("data/projectfiles/UCI HAR Dataset/test/y_test.txt", col.names = "activity")
subject_test <- read.table("data/projectfiles/UCI HAR Dataset/test/subject_test.txt", col.names = "subject")
#Read the features data
features <- read.table("data/projectfiles/UCI HAR Dataset/features.txt")
#Read activity labels data
activityLabels <- read.table("data/projectfiles/UCI HAR Dataset/activity_labels.txt")
colnames(activityLabels) <- c('activityId','activityType')
#combine the respective data in training and test data sets corresponding to subject, label and dataset.
subject <- rbind(subject_train, subject_test)
label <- rbind(train_label, test_label)
dataset <- rbind(train_data, test_data)
#name the columns by transposing the names given in the document features
colnames(dataset) <- transpose(features[2])

#Merges the training and the test sets to create one data set.
MergedData <- cbind(dataset, label, subject)

#Extracts only the measurements on the mean and standard deviation for each measurement. 
column_mean_sd <- grep(".*Mean.*|.*Std.*", names(MergedData), ignore.case=TRUE)
requiredColumns <- c(column_mean_sd, 562, 563)
dim(MergedData)
tidy_data <- MergedData[,requiredColumns]
dim(tidy_data)
str(tidy_data)
#Descriptive data
tidy_data$activity <- as.character(tidy_data$activity)
tidy_data$subject <- as.factor(tidy_data$subject)
for (i in 1:6){
    tidy_data$activity[tidy_data$activity == i] <- as.character(activityLabels[i,2])
}
#descriptive activity names to name the activities in the data set
names(tidy_data)<-gsub("Acc", "Accelerometer", names(tidy_data))
names(tidy_data)<-gsub("Gyro", "Gyroscope", names(tidy_data))
names(tidy_data)<-gsub("BodyBody", "Body", names(tidy_data))
names(tidy_data)<-gsub("Mag", "Magnitude", names(tidy_data))
names(tidy_data)<-gsub("^t", "Time", names(tidy_data))
names(tidy_data)<-gsub("^f", "Frequency", names(tidy_data))
names(tidy_data)<-gsub("tBody", "TimeBody", names(tidy_data))
names(tidy_data)<-gsub("-mean()", "Mean", names(tidy_data), ignore.case = TRUE)
names(tidy_data)<-gsub("-std()", "STD", names(tidy_data), ignore.case = TRUE)
names(tidy_data)<-gsub("-freq()", "Frequency", names(tidy_data), ignore.case = TRUE)
names(tidy_data)<-gsub("angle", "Angle", names(tidy_data))
names(tidy_data)<-gsub("gravity", "Gravity", names(tidy_data))
names(tidy_data)

tidy_data <- data.table(tidy_data)
#independent tidy data set with the average of each variable for each activity and each subject
tidyData <- aggregate(. ~subject + activity, tidy_data, mean)
tidyData <- tidyData[order(tidyData$subject, tidyData$activity),]
write.table(tidyData, file = "Tidy.txt", row.names = FALSE)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
